State of the Art in \\ {\ttlit Twitter Sentiment Analysis}

### 2014-11-27 paper/chapters/2_data.tex
fix author name and twitter

\section{Data}
Twitter is a social network and a microblogging service that
allows their users to compose and read so called 
\emph{tweets}. Each tweet 
is a text message and can contain up to 140 characters
including links, pictures\footnote{pictures are replaced 
by a url targeting a public available image resource}, and special tagged words.
These special words start with a well defined prefix 
and add semantic information to the prefixed word.
Table \ref{tab:twitterprefixes} shows an overview of 
common prefixes supported by twitter and their purpose. 
The hashtag \# tags a special word, also known as hashtag. 
It is used to mark important keywords within the tweet.
There is also a at-sign-prefix \emph{@}, which allows 
to mention other twitter users in a post. It's also possible to 
insert urls as part of the message. Regarding the hard message 
length limitation of a tweet, url-shortener are often used to
 insert longer urls.

>>>>

\section{Data}
Twitter is a social network and a microblogging service that
allows their users to compose and read so called 
\emph{tweets}. Each tweet 
is a text message and can contain up to 140 characters
including links, pictures\footnote{pictures are replaced 
by a url targeting a public available image resource}, and special tagged words.
These special words start with a well defined prefix 
and add semantic information to the prefixed word.
Table \ref{tab:twitterprefixes} shows an overview of 
common prefixes supported by Twitter and their purpose. 
The hashtag \# tags a special word, also known as hashtag. 
It is used to mark important keywords within the tweet.
There is also a at-sign-prefix \emph{@}, which allows 
to mention other Twitter users in a post. It's also possible to 
insert urls as part of the message. Regarding the hard message 
length limitation of a tweet, url-shortener are often used to
 insert longer urls.
